---
title: "P8105_HW3_hb2699"
author: "Han Bao"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(tidyverse)
library(readr)
```

```{r}
# install.packages("devtools")
devtools::install_github("p8105/p8105.datasets")
```


#Question 2
```{r}
# tidy the dataset 
accel<- read_csv(file = "./accel_data.csv") %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    activity_1:activity_1440, 
    names_to = "minute",
    values_to = "activity",
    names_prefix = "activity_", 
  ) %>% 
  mutate(
    day_of_week = recode(day,
                         "Monday" = "Weekday", 
                         "Tuesday" = "Weekday", 
                         "Wednesday" = "Weekday", 
                         "Thursday" = "Weekday", 
                         "Friday" = "Weekday", 
                         "Saturday" = "Weekend", 
                         "Sunday" = "Weekend"))
```

```{r}
nrow(accel)
ncol(accel)
```
The dataset contains 50400 rows and 6 columns.

```{r}
#aggregate the dataset across with minutes
accel %>% 
  group_by(week,day) %>% 
  summarize(total_activity=sum(activity)) %>% 
  knitr::kable(
    caption = "Total activity across minutes")
```

```{r}
accel %>% 
  group_by(minute,day) %>% 
  mutate(minute =as.numeric(minute)) %>% 
  ggplot(aes(x = minute/60, y = activity)) + 
  geom_point(aes(color = day), alpha = .5) + 
   scale_x_continuous(
    breaks = c(0, 3, 6, 9, 12, 15, 18, 21, 24),
    labels = c("0hr", "3hr", "6hr", "9hr", "12hr", "15hr", "18hr", "21hr", "24hr")) + 
  labs(
    title = "Track of Activity Time with one-minute interval",
    x = "Hours",
    y = "Activity",
    caption = "single_panel plot")+
  theme(plot.title = element_text(size=10))
#git push -f
```
From the graph we can see that the most active period of time for the 63-year-old male is between 6am and 12pm and between 15pm and 22pm. The other times during night are lack of activity because he is sleeping and the two hours lack of activity after noon may be because he's tired after the lunch. Besides, he is more active at night in weekdays than in weekends.

#Question 3
```{r}
# install.packages("devtools")
devtools::install_github("p8105/p8105.datasets",force = TRUE)
```

```{r}
library(p8105.datasets)
data("ny_noaa")
```

```{r}
# clean and reform the dataset 
ny_noaa = ny_noaa %>% 
    janitor::clean_names()%>% 
    mutate(ny_noaa, data = as.Date(date)) %>% 
    mutate(year = as.integer(format(date, format = "%Y")),
         month = as.integer(format(date, format = "%m")),
         day = as.integer(format(date, format = "%d"))) %>% 
    mutate(ny_noaa,tmax = as.numeric(tmax)/10) %>% 
    mutate(ny_noaa,prcp = as.numeric(prcp)/10 ) %>% 
    mutate(ny_noaa,tmin = as.numeric(tmin)/10 ) 
```

```{r}
#Find the most common value 
ny_noaa %>% 
  group_by(snow) %>% 
  distinct() %>% 
  summarize(freq = n()) %>% 
  arrange(desc(freq)) %>% 
  filter(!snow== 0) %>% 
  head(1) %>% 
  knitr::kable()
```
The most common depth of snowfall is 25mm which appears 31022 times.

```{r}
#Make a two-panel plot showing the average max temperature in January and in July in each station across years.
#label <- c('01'='January', '07'='July')
 ny_noaa %>% 
   filter(month == 1| month == 7) %>% 
   mutate(month = month.abb[month]) %>% 
   filter(!is.na(tmax)) %>% 
   mutate(tmax = as.numeric(tmax)) %>% 
   group_by(month,year,id) %>% 
   summarise(mean_month = mean(tmax)) %>% 
   ggplot(aes(
     x=factor(year),
     y=mean_month,
     color=year))+
   geom_point() +
  facet_grid(.~month)+
  ggtitle('The mean max temperature in January and July in each station across years')+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
The temperature in January have a slow trend of climbing as the year pass and in 1993, 2002, and 2003 it was a little off the trend but not too much to be considered as an outlier. For Temperature in July, the trend is not as obvious and also no obvious outlier is observed.